### 2019-05-21 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Complete:  is almost sparse

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_h}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \m {\Rm {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse

@@

We apply DS to find \m {\hat {\V {g}}}, setting
\Disp {
\NC \g 
= \NC \R {2 \log N_h} \NR[+]
}

@@

Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
Let \m {S:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
\Disp {
\NC \Nm {S \RB {x} \DB {n_1}} \geq  \NC \Nm {S \RB {x} \DB {n_2}}, \NR[+]
\NC n_1 > \NC n_2,
\quad n_1, n_2 \in T\RB {N} \NR
}

Denote the sorting function to be \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}.
That is, for \m {x \in \MB {V}_{\MB {K}} \SB {N}}, \m {x} is confined in sorted magnitude according to \m {f}.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), the order is irrelevent.
Formally,
\Disp {
\NC \Nm {\MC{S} \SB {x} \DB {n} }
\leq \NC f \SB {n},
\quad n \in T \RB {N}. \NR
}

\Result
{Definition}
{
For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
\Disp {
\NC \sum_{n=s}^N \Nm {\MC{S} \SB {\V {x}} \SB {n}}
\leq \NC R. \NR
}
}

\Result
{Lemma}
{
Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
\Disp {
\NC R
= \NC \F {1}{\pi} \log \F {N_H}{L-1}. \NR
}
}

We now show the lemma, which is the key to bounding the sparsity of \m {h}.
Let \m {\f'} be fixed.
What we have to bound is
\Disp {
\NC R \SB {\f'}
=\NC \sum_{n_H =s}^{N_H -1}
   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} \NR[+]
}
Observe
\Disp {
\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
=\NC \F {1}{N_H} D \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
}
where \m {D} is the Dirichlet kernel
\Disp {
\NC D \SB {\f'}
:= \NC \Nm { \sum_{n_H=0}^{N_H-1} \Rm {e}^{i n_H \f'} } \NR
\NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
Now, it can be verified that
\Result
{Lemma}
{
For \m {-\pi \leq x < \pi}, we have
\Disp {
\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
}
}
Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
\Disp {
\NC \Nm {D \SB {\f'} }
\leq \NC B \SB {\f'} \NR
\NC := \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}} \NR[+]
\NC -\pi \leq \NC \f' < \pi. \NR
}
Thus,
\Disp {
\NC R \SB {\f'}
=\NC \sum_{n_H =s}^{N_H -1}
   \F {1}{N_H}
   \MC{S}
   \SB {
      \sum_{n_H' =s}^{N_H -1}
      B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
      \V {u}_{n_H'}
   }
   \DB {n_H}
\NR[+]
}
Notice that \m {\Nm {B \SB {\phi'}}} is monotone, and then
\Disp{
\NC \NC \MC{S}
\SB {
   \sum_{n_H' =s}^{N_H' -1}
   B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
   \V {u}_{n_H'}
}
\DB {n_H} \NR
\NC =\NC B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
\NC \leq \NC B \SB {\F {2 \pi n_H} {N_H}} \NR[+]
}
What we saw gives
\Disp{
\NC R \SB {\f'}
=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1}
   B \SB {\F {2 \pi n_H} {N_H}} \NR
}

By the approximation of rectangle to integral,
\Disp {
\NC R\SB {\eta} -\F {2\pi} {N_H}
\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D\SB {\f'}} d \f' \NR
}
Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{\RB {24 -\f'^2} \f'} d \f'
+\F {2\pi} {N_H} \NR
\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
-\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
+\F {2\pi} {N_H}
}
Notice the argument of log in the second term \m {<1}, and we drop that.
Also drop \m {2\pi /N_H} since it is small.
Furthermore the \m {2\pi} factor in log can be dropped too.
\Disp {
\NC R\SB {\f}
\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
}

@@

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
=\NC \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
  } ^2
}
\NR[+]
}
Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
Also notice that
\Disp{
\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
\NC = \NC 0 \NR[+]
}
Having said that, with straightforward calculation, we see that the remaining terms are
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
\NC = \NC
\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
\Nm {\V{u} \DB{n_Y}} ^4 \NR
\NC \NC \quad \quad
+\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
\sum _{n_Y =0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R, n_R' =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
}
Plugging in the moments, we have
\Disp{
\NC =\NC -\F{3}{2} \RB {1 -\F{1}{N_R}} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3 +\F{1}{N_R}} \VNm {\V{u}} _2 ^4 \NR[+]
}
Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
\Disp{
\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}

@@

\startsection [title={Mean Square Error Analysis for Complex DS}]

>>>>

Our plan is first to show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.

@@

Let \m {\hat {\V {g}}} be the Dantzig Selector.
For concreteness, we set
\Disp {
\NC \g 
= \NC \R {2 \log N_h} \NR[+]
}

@@

Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.

And Denote the sorting function to be \m {\MC {S}:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
\Disp {
\NC \Nm {\MC {S} \SB {\V{x}} \DB {n_1}} \geq \NC \Nm {\MC {S} \SB {\V{x}} \DB {n_2}}, \NR[+]
\NC n_1 \leq \NC n_2,
\quad n_1, n_2 \in T\RB {N} \NR
}
That is, \m {\V{x}} is sorted in magnitude.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), the order is irrelevent.

\Result
{Definition}
{
For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
\Disp {
\NC \Nm {\RB {\MC{S} \SB {\V {x}} \SB {n}} \DB {s:N}}_p
\leq \NC R. \NR[+]
}
}

Let \m {\f} be fixed.
What we have to bound is
\Disp {
\NC R^2
=\NC \sum_{n_H =s}^{N_H -1}
   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} ^2 \NR[+]
}

Introduce
\Disp {
\NC \psi \SB {\f, n_H}
:=\NC \RB {
   \RB {
      \RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}}
      +\F {2 \pi n_H} {N_H}
      +\pi
   } \;
   \Rm{mod}\; \RB {2\pi}
}
-\pi
}
so that
\Disp{
\NC \Nm {\psi \SB {\f, n_H}}
\leq \NC \pi
}
And define \m {D} to be the Dirichlet kernel
\Disp {
\NC D \SB {\psi'}
:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
\NC \quad 0 \leq \NC  \psi' \leq \pi \NR
}
Then observe
\Disp {
\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
=\NC \F {1}{N_H} D \SB {\psi \SB {\f, n_H}} \NR
}

Now, it can be verified that
\Result
{Lemma}
{
For \m {-\pi \leq x < \pi}, we have
\Disp {
\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
}
}
Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
\Disp {
\NC \Nm {D \SB {\psi'} }
= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
\NC \leq \NC B \SB {\psi'} \NR
\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR[+]
\NC -\pi \leq \NC \psi' < \pi. \NR
}
Thus,
\Disp {
\NC R^2
=\NC \F {1}{N_H^2}
\sum_{n_H =s}^{N_H -1}
\MC{S} \SB {
   \sum_{n_H' =0}^{N_H -1}
   B \SB {\psi \SB {\f, n_H'}}
   \V {u}_{n_H'}
}
\DB {n_H} ^2 \NR[+]
}
Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We seek to bound the ``rectangulars'' with an integral, and we have to split the cases that \m {N_H} is odd and even.
Anyway, a moment's reflection shows
\Disp {
\NC R^2
\leq \NC \F {1}{N_H^2} \D \F {N_H}{2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
\NC = \NC \F {2304} {N_H \pi^6}
\int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
\NC =\NC \F{1} {2\pi^2}
\RB {
  -\F {8} {u}
+\F {4\pi^2 u} {24 -\pi^2 u^2}
+\R{6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R{6}}}
}
\Bigg \| _{s/N_H} ^1 \NR
\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +0.032670 \NR[+]
}
In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.

In summary,

\Result
{Lemma}
{
Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
Then \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
\Disp {
\NC R
= \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {1} {62}. \NR[+]
}
}

\stoptext

@@

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
=\NC \MB{E} \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
  } ^2
}
\NR[+]
}
Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
Also notice that
\Disp{
\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
\NC = \NC 0 \NR[+]
}
Having said that, with straightforward calculation, we see that the remaining terms are
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
\NC = \NC
\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
\Nm {\V{u} \DB{n_Y}} ^4 \NR
\NC \NC \quad \quad
+\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
\sum _{n_Y =0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R, n_R' =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
}
Plugging in the moments, we have
\Disp{
\NC =\NC -\F{3}{2} \RB {1 -\F{1}{N_R}} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3 +\F{1}{N_R}} \VNm {\V{u}} _2 ^4 \NR[+]
}
Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
\Disp{
\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}

@@

\startsection [title={Expected Square Error for Complex-Case DS}]
